\textbf{ Accurate spectroscopic estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-22 paper/sp.tex
document tweaks; assumptions

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing

\title{Accurate spectroscopic estimates of luminosity and distance\\
       for luminous red-giant stars}

\correspondingauthor{Anna-Christina Eilers}
\email{eilers@mpia.de}

@@

\keywords{%
methods:~statistical
 ---
techniques:~spectroscopic
 ---
catalogs
 ---
surveys
 ---
parallaxes
 ---
stars:~distances
 ---
Galaxy:~disk
 ---
infrared:~stars
}

@@

@@

\section{Validation}

\section{Results and Discussion}

>>>>

% tweak the modern style -- trust in Hogg
\setlength{\parindent}{1.0\baselineskip}
\addtolength{\textheight}{0.5in}
\addtolength{\topmargin}{-0.3in}

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust in Hogg

\title{\textbf{%
Accurate spectroscopic estimates of luminosity and distance\\
for luminous red-giant stars%
}}

@@

\keywords{%
methods:~statistical
 ---
techniques:~spectroscopic
 ---
catalogs
 ---
surveys
% ---
%parallaxes
 ---
stars:~distances
 ---
Galaxy:~disk
 ---
infrared:~stars
}

@@

\section{Assumptions of the method}

Our position is that a methodological technique is correct inasmuch as
it delivers correct or best results \emph{under its particular assumptions}.
In that spirit, we present here the assumptions of the method
explicitly.
We will return to these assumptions in the Discussion section below,
to address the costs and benefits of each in more depth.
\begin{description}
\item[features] bar

\item[good features] bar

\item[representativeness] bar

\item[sparsity] bar

\item[linearity] bar

\item[likelihood] bar
\end{description}

@@

\section{Results and validation}

\section{Discussion}
